\sys: Light-touch Data-Parallel Shell Processing

### 2020-10-09 paper/draft.tex
Add text for short-combined
Thin down hightlights as Ben mentioned

\noindent
As the first and third columns are suppressed, \ttt{comm} can be categorized in \sta by regarding its first file argument as a static ``configuration'' input;
% NV: I don't think this is correct, because the small input might be the other argument;  you could even have `comm - -`
  this input accompanies every replicated instance of the command executing in parallel.
The second clause is symmetric to the first with respect to the second input. 
The third clause is the general case, classifiying \ttt{comm} in \pur, as \ttt{comm} needs to read both inputs completely before outputing its results.
Option \ttt{stdin-hyphen} indicates that \ttt{-} represents standard input if given as a file argument.
% The third clause is the general case, which includes \ttt{comm} invocations without any options, and is captured by the third clause.
% There, \ttt{comm} is classified as \pur as it needs to % wait until it 
%   read both inputs completely before it can output its results.
% Its inputs are its first and second file arguments (\ie excluding any options), and its output is produced in \ttt{stdout}.

@@

\heading{Highlights}
This paragraph highlights results for \ttt{width=16}, but \sys's evaluation reports on varying \ttt{width}s (2--64).
% The vast majority (39/44) of scripts---all unmodified---see significant speedups (average over all is $6.7\times$, up to $61\times$).
Overall, \sys accelerates 39/44 scripts---all unmodified---by 1.92--17.42$\times$; 
  for the rest, the parallel performance is comparable to the sequential (0.89, 0.91, 0.94, 099, 1.01$\times$).
  % \kk{eurosys: I have an issue that I am not sure how to address. I would like to have the 61.1x here (which is due to 64 width)  but I don't see a good way of including it without sounding suspicious.}
For a subset of our benchmarks~\sx{ours}, we decouple the speedup due to \sys's DFG transformations alone from the one achieved when including its runtime primitives:
  the former averages $5.9\times$, jumping to $8.6\times$ due to the latter.
A different subset ($30$ benchmarks) sees average speedups of $6.02\times$~\sx{unix50}.
% , depending on the classed of commands involved
Two complex scripts with 15~\sx{macro1} and 34~\sx{macro2} commands written in multiple languages see speedups of $2.44\times$ and $12.7\times$.
\sys significantly outperforms \ttt{sort --parallel}, a hand-tuned parallel implementation, and performs better than GNU \ttt{parallel}, which returns incorrect results if used without care~\sx{micro}.
% Averages: [1.955223776839714, 3.478591807121036, 5.721328556478535, 8.604380509595906, 10.666921423438112, 13.246864076708423]
% No Eager Averages: [1.6327834370824543, 2.5481043878162444, 3.8623841529643173, 5.931851620007484, 7.466566647963421, 9.35752032439642]
% From the rest, only two see a slowdown, only because \sys's setup ($\sim1s$) is higher than their runtime ($\sim0.4s$).
% \sys's optimized primitives offer benefits even against manually parallelized scripts. % (such as GNU sort, and GNU parallel).
% \sys's compilation pass is negligible (avg. $<1s$). %  for non trivial program execution.
% In two large cases, tasks such as data download, extraction, and preprocessing---often implemented using shell scripts and outside the focus of specialized parallelization frameworks---take comparable time to the execution of the main computation, and can be significantly accelerated by \sys.
% In terms of manual effort,

>>>>

\noindent
As the first and third columns are suppressed, \ttt{comm} can be categorized in \sta by regarding its first file argument as a static ``configuration'' input;
% NV: I don't think this is correct, because the small input might be the other argument;  you could even have `comm - -`
  this input accompanies every replicated instance of the command executing in parallel.
The second clause is symmetric to the first with respect to the second input. 
The third clause is the general case, classifiying \ttt{comm} in \pur, as \ttt{comm} needs to read both inputs completely before outputing its results.
Option \ttt{stdin-hyphen} indicates that \ttt{-} represents standard input if given as a file argument, and option \ttt{short-combined} indicates that flags can be combined, as in \ttt{comm -13}.
% The third clause is the general case, which includes \ttt{comm} invocations without any options, and is captured by the third clause.
% There, \ttt{comm} is classified as \pur as it needs to % wait until it 
%   read both inputs completely before it can output its results.
% Its inputs are its first and second file arguments (\ie excluding any options), and its output is produced in \ttt{stdout}.

@@

\heading{Highlights}
This paragraph highlights results for \ttt{width=16}, but \sys's evaluation reports on varying \ttt{width}s (2--64).
% The vast majority (39/44) of scripts---all unmodified---see significant speedups (average over all is $6.7\times$, up to $61\times$).
Overall, applying \sys to all 44 unmodified scripts accelerates 39 of them by 1.92--17.42$\times$; for the rest, the parallel performance is comparable to the sequential (0.89, 0.91, 0.94, 099, 1.01$\times$). The total average speedup over all 44 benchmarks is $6.7\times$.
\sys's runtime primitives offer significant benefits---for the 10 scripts that we measured with and without the runtime primitives they bump the average speedup from $5.9\times$ to $8.6\times$.
% Overall, \sys accelerates 39/44 scripts---all unmodified---by 1.92--17.42$\times$; 
  % for the rest, the parallel performance is comparable to the sequential (0.89, 0.91, 0.94, 099, 1.01$\times$).
  % \kk{eurosys: I have an issue that I am not sure how to address. I would like to have the 61.1x here (which is due to 64 width)  but I don't see a good way of including it without sounding suspicious.}
% For a subset of our benchmarks~\sx{ours}, we decouple the speedup due to \sys's DFG transformations alone from the one achieved when including its runtime primitives:
  % the former averages $5.9\times$, jumping to $8.6\times$ due to the latter.
% A different subset ($30$ benchmarks) sees average speedups of $6.02\times$~\sx{unix50}.
% Two complex scripts with 15~\sx{macro1} and 34~\sx{macro2} commands written in multiple languages see speedups of $2.44\times$ and $12.7\times$.
\sys significantly outperforms \ttt{sort --parallel}, a hand-tuned parallel implementation, and performs better than GNU \ttt{parallel}, which returns incorrect results if used without care~\sx{micro}.
% Averages: [1.955223776839714, 3.478591807121036, 5.721328556478535, 8.604380509595906, 10.666921423438112, 13.246864076708423]
% No Eager Averages: [1.6327834370824543, 2.5481043878162444, 3.8623841529643173, 5.931851620007484, 7.466566647963421, 9.35752032439642]
% From the rest, only two see a slowdown, only because \sys's setup ($\sim1s$) is higher than their runtime ($\sim0.4s$).
% \sys's optimized primitives offer benefits even against manually parallelized scripts. % (such as GNU sort, and GNU parallel).
% \sys's compilation pass is negligible (avg. $<1s$). %  for non trivial program execution.
% In two large cases, tasks such as data download, extraction, and preprocessing---often implemented using shell scripts and outside the focus of specialized parallelization frameworks---take comparable time to the execution of the main computation, and can be significantly accelerated by \sys.
% In terms of manual effort,
